\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-02-01 paper.qmd
Changed the point size of trimesh

#tSNE_pbmc <- read_rds("data/pbmc/pbmc_tsne_30.rds")
UMAP_pbmc <- read_rds("data/pbmc/pbmc_umap_15_min_dist_0.99_metric_euclidean.rds")
# PHATE_pbmc <- read_rds("data/pbmc/pbmc_phate.rds")
# TriMAP_pbmc <- read_rds("data/pbmc/pbmc_trimap.rds")
# PaCMAP_pbmc <- read_rds("data/pbmc/pbmc_pacmap.rds")

@@

@@

@@

```{r}
#| echo: false
#| fig-cap: "(a) 2D layout from UMAP (n_neighbors = 15, min_dist = 0.99, metric = euclidean) applied for the PBMC3k dataset. Is this a best representation of the original data?, (b)  Model in the 2D space with UMAP (<>)"
#| label: fig-nldervisPBMCUMAP2
#| out-width: 100%
#| fig-pos: h

#plot_list2_pbmc + 
trimesh_removed_pbmc_umap + plot_list2_pbmc_error +
plot_layout(guides='collect', ncol=3) &
  theme(legend.position='bottom')

@@

trimesh_removed_pbmc_umap <- trimesh_removed_pbmc_umap +
  geom_point(size = 0.01, colour = "#33a02c") +
  #ggtitle("(b)") +
  theme_linedraw() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  annotate(geom = 'text', label = 'b', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3)

>>>>

#tSNE_pbmc <- read_rds("data/pbmc/pbmc_tsne_30.rds")
UMAP_pbmc <- read_rds("data/pbmc/pbmc_umap_15_min_dist_0.99_metric_cosine.rds")
# PHATE_pbmc <- read_rds("data/pbmc/pbmc_phate.rds")
# TriMAP_pbmc <- read_rds("data/pbmc/pbmc_trimap.rds")
# PaCMAP_pbmc <- read_rds("data/pbmc/pbmc_pacmap.rds")

@@

```{r}
#| warning: false
#| echo: false
shape_value_pbmc <- calculate_effective_shape_value(.data = UMAP_pbmc,
                                                      x = UMAP1, y = UMAP2) ## 0.8772751

@@

trimesh_removed_pbmc_umap <- trimesh_removed_pbmc_umap +
  geom_point(size = 0.005, colour = "#33a02c") +
  #ggtitle("(b)") +
  theme_linedraw() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  annotate(geom = 'text', label = 'b', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3)

@@

```{r}
#| echo: false
#| fig-cap: "(a) 2D layout from UMAP (n_neighbors = 15, min_dist = 0.99, metric = cosine) applied for the PBMC3k dataset. Is this a best representation of the original data?, (b)  Model in the 2D space with UMAP (<>)"
#| label: fig-nldervisPBMCUMAP2
#| out-width: 100%
#| fig-pos: h

@@

trimesh_removed_pbmc_umap <- trimesh_removed_pbmc_umap +
  geom_point(size = 0.005, colour = "#33a02c") +
  #ggtitle("(b)") +
  theme_linedraw() +
  theme(plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank()) +
  annotate(geom = 'text', label = 'b', x = -Inf, y = Inf, hjust = -0.5, vjust = 1.5, size = 3)

### 2024-02-01 paper.tex
Changed the point size of trimesh

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[sharp corners, interior hidden, boxrule=0pt, frame hidden, borderline west={3pt}{0pt}{shadecolor}, enhanced, breakable]}{\end{tcolorbox}}\fi

@@

\caption{\label{fig-nldervisPBMCUMAP2}(a) 2D layout from UMAP
(n\_neighbors = 15, min\_dist = 0.99, metric = euclidean) applied for
the PBMC3k dataset. Is this a best representation of the original data?,
(b) Model in the 2D space with UMAP (\textless\textgreater)}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, sharp corners, borderline west={3pt}{0pt}{shadecolor}, enhanced, boxrule=0pt, frame hidden, interior hidden]}{\end{tcolorbox}}\fi

@@

\caption{\label{fig-nldervisPBMCUMAP2}(a) 2D layout from UMAP
(n\_neighbors = 15, min\_dist = 0.99, metric = cosine) applied for the
PBMC3k dataset. Is this a best representation of the original data?, (b)
Model in the 2D space with UMAP (\textless\textgreater)}
